An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-21 poly-embed-journal/poly-embed-journal.tex
meeting notes 1

\begin{claim}
	For all $x\in\reals^\Y_+$, there exists $v^*\in\V^*$ such that $H_{v^*}$ supports $G$ at $(x,g(x))$.
\end{claim}
\begin{proof}
We can write any face $F_v = H_v \cap G = \{x \in \reals_+^{d-1} \mid \inprod{x}{v} = g(x)\}$.
Since $H_v^+$ must be a valid halfspace to define a face, we know that $G \subseteq H_v^+$.
%If there was no $v \in \V^*$ such that $x \in F_v$, 
Since $\H^* = \H_\Y \cup \H_{\V^*}$, if there was no $v \in \V^*$ such that $x \in F_v$, it must be the case that $\min_{H_v \in \H_\Y} \inprod{v}{x} = \min_{y \in \Y} x_y = g(x) = 0$ by construction of the halfspaces in $\H_\Y$. %, and we must have $x \not \in \reals_{++}^\Y$.

\jessie{If $g$ is not locally constant}
Since $g$ is continuous on $\reals^d_+$ (as it is convex), and not constant \jessie{??}, there must be some $x' \in B(x,\epsilon) \cap \reals_+^\Y$ such that $g(x') > 0$ and therefore no $y \in \Y$ would define a face $F_{v^*}$ supporting $G$ at $x'$.
(We know such a face exists as $G$ is polyhedral and finite.)
That $v^*$ must then be in $\V^*$, and we claim $\inprod{v^*}{x} = 0$, which would imply $H_{v^*}$ also supports $G$ at $x$.
If $\inprod{v^*}{x} > 0 = g(x)$ (recall $g$ nonnegative on $\reals_+^\Y$) then we contradict continuity of $g$ on $\reals_+^\Y$. 
Therefore, we must have $\inprod{v^*}{x} = 0$, and thus $H_{v^*}$ also supports $G$ at $x$.
\jessie{Not the level of rigor that we want.  Also using lots of polyhedral structure here.}
%First, $\inprod{v^*}{x} \geq 0$ by definition of $g$ nonnegative on $\reals_+^\Y$, and $\leq 0$

@@

@@

\begin{claim} 
For all $v\in\reals^\Y_+$, if $H_v$ supports $G$,  $\dim(\pi(F_v)) = \dim(F_v)-1$.
\end{claim}
\begin{proof}
	By assumption, $G$ is nowhere locally constant, meaning $([\vec 0; -1], b) \not \in \V^*$ for any $b \in \reals$.
	Therefore, the dimension of $\pi(F_v) = \pi(H_v \cap G) = \pi(\{(x,c) \in G \mid \inprod{v}{x} = c, c = g(x) \}) = \{x \in \reals^d_+ \mid \inprod{v}{x} = c\}$.
	Any $k\leq d$ vectors $\{z_i\}_{i=1}^k$ forming a basis for $\{(x,c) \in G \mid \inprod{v}{x} = c, c = g(x) \}$ \jessie{....}

	\jessie{TODO}
	Facts we can potentially use:
	$F_v = \H_v \cap G \neq \emptyset$ by assumption.
	$\dim(F_v) = \dim(\affhull(F_v))$
	$\dim(\pi(F_v)) = \dim(F_v) - 1$.
\end{proof}

@@

\begin{claim}
	For any $v \in \V$, the face $F_{v}$ must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
	\jessie{I don't think this is true as stated.  I think this is true for non-facets, but this implies that any $H_y \in \H_\Y$ doesn't support $G$}
\end{claim}
\begin{proof}
%	Suppose $F_v \subseteq F_{v^*}$.
%	If $v' \not \in \V^*$, then $v' = [e_y; 0]$ for some $y \in \Y$.
%	By construction of $G$, the polyhedron shoots off to $-\infty$, so the only subfaces of $F_{v'}$ are also adjacent 
%	\jessie{Very informal...} 
\end{proof}

>>>>

\begin{claim}
	For all $x\in\reals^\Y_+$, there exists $v^*\in\V^*$ such that $H_{v^*}$ supports $G$ at $(x,g(x))$.
\end{claim}
\begin{proof}
%We can write any face $F = H \cap G = \{(x',c) \in \reals_+^{d} \mid \inprod{x'}{v} = c = g(x')\}$.
%Since $H_v^+$ must be a valid halfspace to define a face, we know that $G \subseteq H_v^+$.
%%If there was no $v \in \V^*$ such that $x \in F_v$, 
%Since $\H^* = \H_\Y \cup \H_{\V^*}$, if there was no $v \in \V^*$ such that $x \in F_v = F$, it must be the case that $\min_{H_v \in \H_\Y} \inprod{v}{x} = \min_{y \in \Y} x_y = g(x) = 0$ by construction of the halfspaces in $\H_\Y$. %, and we must have $x \not \in \reals_{++}^\Y$.
%
%\jessie{If $g$ is not locally constant}
%Since $g$ is continuous on $\reals^d_+$ (as it is convex), and not constant \jessie{??}, there must be some $x' \in B(x,\epsilon) \cap \reals_+^\Y$ such that $g(x') > 0$ and therefore no $y \in \Y$ would define a face $F_{v^*}$ supporting $G$ at $x'$.
%(We know such a face exists as $G$ is polyhedral and finite.)
%That $v^*$ must then be in $\V^*$, and we claim $\inprod{v^*}{x} = 0$, which would imply $H_{v^*}$ also supports $G$ at $x$.
%If $\inprod{v^*}{x} > 0 = g(x)$ (recall $g$ nonnegative on $\reals_+^\Y$) then we contradict continuity of $g$ on $\reals_+^\Y$. 
%Therefore, we must have $\inprod{v^*}{x} = 0$, and thus $H_{v^*}$ also supports $G$ at $x$.
%\jessie{Not the level of rigor that we want.  Also using lots of polyhedral structure here.}
%%First, $\inprod{v^*}{x} \geq 0$ by definition of $g$ nonnegative on $\reals_+^\Y$, and $\leq 0$

\jessie{Notes in meeting:
	For any $x \in \reals^d_+$, consider $v^* \in \argmin_{v \in \V} \inprod{v}{x}$.
Argue $G \subseteq H^+_{v^*}$ by definition.
Argue support: $g(x) = \inprod{v^*}{x}$.  WTS $(x,g(x)) \in G$.  Already have $(x,g(x)) \in H_{v^*}$.}

@@

\raf{For Lemma X: NTS $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+ \implies \V^* \subseteq \V$.}
\raf{If $G = \cap( \H_\Y \cup \H_\V)$...}

@@

\begin{claim} 
For all $v\in\reals^\Y_+$, if $H_v$ supports $G$, then $\dim(\pi(F_v)) = \dim(F_v)$.
\end{claim}
\begin{proof}
	By assumption, $G$ is nowhere locally constant, meaning $([\vec 0; -1], b) \not \in \V^*$ for any $b \in \reals$.
	Therefore, the dimension of $\pi(F_v) = \pi(H_v \cap G) = \pi(\{(x,c) \in G \mid \inprod{v}{x} = c, c = g(x) \}) = \{x \in \reals^d_+ \mid \inprod{v}{x} = c\}$.
	Let $A := \{(x,c) \in G \mid \inprod{v}{x} = c, c = g(x) \}$
	If $\dim(A) = k$, then there is a set of $k\leq d$ vectors $\{z_i\}_{i=1}^k$ forming a basis for $\affhull(A)$.
	In particular, \jessie{....}

	\jessie{TODO}
	Facts we can potentially use:
	$F_v = \H_v \cap G \neq \emptyset$ by assumption.
	$\dim(F_v) = \dim(\affhull(F_v))$
	$\dim(\pi(F_v)) = \dim(F_v) - 1$.
	\jessie{Think of the projection as a linear map and affine hull as a subspace.   Pick any point in relint of the facet, at the linear span, ...}
	\jessie{$\affhull(F_v) = H_v$, $\dim(\affhull(\pi(F_v))) = \dim(\pi(\affhull(F_v)))$.   Show that when you project $H_v$, it gives you $\reals^\Y$.}

	\jessie{Meeting notes: just need to argue that you never needed $c$ (i.e., $c$ was always just $g(x)$).  Maybe: take an affine basis, project, and show it's an affine basis. Given $\Y+1$ affinely independent vectors $z_i$ in $F_v$, so we get $|\Y| = 1$ affinely independent vectors.  Claim: $\{\pi(z_i)\}$ are affinely independent.
	Let $a_1, \ldots, a_{\Y+1}$ sum to $0$, such that $\sum_i a_i \pi(z_i) = 0$.
	Want to conclude $a_i = 0$ for all $i$.

	Observe $z_i = (x_i, \inprod{v}{x_i})$ for all $i$ since $z_i \in F_v$, and therefore in $H_v$.
	So $0 = \sim_i a_i \pi(z_i) = \sum_i a_i x_i$.

	Moreover, the sum $\sum_i a_i z_i = \sum_i a_i (x_i, \inprod{v}{x_i}) = (\sum_i a_i x_i, \inprod{v}{\sum_i a_i x_i}) = (0,0) = \vec 0$.
	Thus, since the set $\{z_i\}$ is affinely independent, we have $a_i = 0$ for all $i$.
}
\end{proof}

@@

\begin{claim}
	For any $v \in \V$, the face $F_{v}$ must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
	\jessie{I don't think this is true as stated.  I think this is true for non-facets, but this implies that any $H_y \in \H_\Y$ doesn't support $G$}
\end{claim}
\begin{proof}
Since every face of a convex polyhedron is a convex polytope, any $F_v$ is 
\end{proof}
